ML-based approach for accelerating global search algorithm for solving multicriteria problems\thanks{Supported by organization x.}

### 2022-02-07 2022/LION/main.tex
LION PD->PS

\begin{equation}
R(i)=R_{ags} (i)+ \alpha R_{PD} (i).
\label{eq:5}
\end{equation}

The term $R_{ags}(i)$ allows you to select a subinterval oriented at finding the global minimum of the current optimization task (\ref{eq:4}), while $R_{PD}(i)$ influences the selection of a subinterval to improve the evaluation of the Pareto area. The coefficient $\alpha$ from (\ref{eq:5}) allows adjusting the contribution of each of parts.

@@

Calculation of $R_{PD}(i)$ is based on machine learning methods. When solving the first global search problem (\ref{eq:4}), the value of $R_{PD}(i)$ is assumed to be zero. To solve each subsequent scalar problem (\ref{eq:4}), $R_{PD}(i)$ is calculated as follows.

In the course of Pareto set assessment all trial points are partitioned into two classes. This bipartition is based on belonging to the Pareto set. For these classes, a separation hyperplane is constructed in the domain of criteria values using the logistic regression \cite{Yu2011}. Examples of separated planes are shown in Fig. \ref{fig:1}. During the choice of a new trial point, the distances of all obtained criteria values from the separated plane are calculated and the value of $R_{PD}(i)$ is built depending on these distances.

>>>>

\begin{equation}
R(i)=R_{ags} (i)+ \alpha R_{PS} (i).
\label{eq:5}
\end{equation}

The term $R_{ags}(i)$ allows you to select a subinterval oriented at finding the global minimum of the current optimization task (\ref{eq:4}), while $R_{PS}(i)$ influences the selection of a subinterval to improve the evaluation of the Pareto area. The coefficient $\alpha$ from (\ref{eq:5}) allows adjusting the contribution of each of parts.

@@

Calculation of $R_{PS}(i)$ is based on machine learning methods. When solving the first global search problem (\ref{eq:4}), the value of $R_{PS}(i)$ is assumed to be zero. To solve each subsequent scalar problem (\ref{eq:4}), $R_{PS}(i)$ is calculated as follows.

In the course of Pareto set assessment all trial points are partitioned into two classes. This bipartition is based on belonging to the Pareto set. For these classes, a separation hyperplane is constructed in the domain of criteria values using the logistic regression \cite{Yu2011}. Examples of separated planes are shown in Fig. \ref{fig:1}. During the choice of a new trial point, the distances of all obtained criteria values from the separated plane are calculated and the value of $R_{PS}(i)$ is built depending on these distances.
